Opportunities for improvement in adult trauma patients admitted to the intensive care unit: A registry-based study

### 2024-03-09 manuscript.Rmd
9/3

There were ... patients in the trauma registry between January 1 2014
and February 1 2023. ... with trauma team activation regardless of ISS
score, ... patients admitted without trauma team activation but with ISS
score \> 9. .... patients were included in the morbidity and mortality
screening process between 2014 and 2022. ... of these patients were also
admitted to the ICU. ... patients were excluded as they were younger
than 15 years and ... patients were excluded because they were dead on
arrival. This leaves us with 167 outcomes.

@@

# Results

14,022 patients were included in the trauma registry and trauma care
quality database between 2017 and 2023. 12,278 patients were excluded,
leaving a total of 1,744 patients eligible for the study. 11,343 were
excluded because they were not treated in the ICU. 3 patients were
excluded because they were under 15 years old. 6 patients were excluded
because they were dead on arrival, and 926 patients were excluded
because there was no data on the presence or absence OFI.

[n] patients were excluded because there was missing data, leaving a
total of [n] patients included in the study.

Table 1 present sample characteristics. [n{%}] patients were male and
[n{%}] patients were female. [n{%}] patients had no intubation. Most
patients of the intubated ones were intubated for xx days [n{%}]. The
number of patients who arrived outside working hours - on Saturday or
Sunday or after 5 pm or before 8 am were [n{%}]. [n{%}] patients had an
ASA-score of 1-2 before arrival to the hospital, and [n{%}] patients had
an ASA-score of 3-7 before arrival to the hospital. [n{%}] patients died
within 30 days after hospitalization.

Table 2 shows the unadjusted and adjusted associations of the selected
patient and process factors in relation to OFI. In the unadjusted
analysis the factors that were significantly associated with the
presence of OFI were: ... Male
`r inline_text(table3a, variable = Sex, level = "Male")` Female
`r inline_text(table3a, variable = Sex, level = "Female")` Age
`r inline_text(table3a, variable = Age)` No intubation
`r inline_text(table3a, variable = Intubation, level = "No intubation")`
Respiratory rate `r inline_text(table3a, variable = RespiratoryRate)`
Systolic blood pressure
`r inline_text(table3a, variable = SystolicBloodPressure)` Glasgow Coma
Scale `r inline_text(table3a, variable = GlasgowComaScale)` Jour
`r inline_text(table3a, variable = Jour, level = "Yes")` Time to first
CT `r inline_text(table3a, variable = TimeFCT)` Time to first
intervention `r inline_text(table3a, variable = TimeFInt)` ASA preinjury
1-2 `r inline_text(table3a, variable = ASApreinjury, level = "ASA 1-2")`
Death within 30 days
`r inline_text(table3a, variable = Survival, level = "Dead")`

In the adjusted analysis the following factors demonstrated significant
association with OFI: ...

x was significantly associated with increased odds of OFI in both the
unadjusted and adjusted analyses.

x were not significantly associated with OFI in the unadjusted or the
adjusted analyses.

@@

We found that --- was associated with higher odds of OFI. Previous
research ...

@@

\-- was associated with OFI in the unadjusted analysis but not in the
adjusted analysis.

@@

The study is conducted on --- outcomes. There were few outcomes because
we included only those who were admitted to the ICU, \> 14 years old,
not dead on arrival and had a registration for the presence or absence
of OFI. The external validity is therefore compromised due to the
limited size of the Swedish database. However, ...

>>>>

There were 14,022 patients in the trauma registry between January 1 2014
and February 1 2023. 2679 of these patients were 
admitted to the ICU. 3 patients were then excluded as they were younger
than 15 years and 6 patients were excluded because they were dead on
arrival. 928 patients were excluded because there was no registration on whether there was an OFI or not. 293 patients were excluded because they had missing values in one or more variables.
This leaves us with 143 outcomes for OFI, and 1,306 outcomes for "No OFI".

#Detta blir upprepning då det redan står längre ner i resultatdelen?

@@

# Results
```{r}
library(gtsummary)
source("main.R")
```

14,022 patients were included in the trauma registry and trauma care
quality database between 2017 and 2023. 12,278 patients were excluded,
leaving a total of 1,742 patients eligible for the study. 11,343 were
excluded because they were not treated in the ICU. 3 patients were
excluded because they were under 15 years old. 6 patients were excluded
because they were dead on arrival, and 928 patients were excluded
because there was no data on the presence or absence OFI.

293 patients were excluded because there was missing data, leaving a
total of 1,449 patients included in the study.

Table 1 present sample characteristics. 1,096 (76%) patients were male and 353 (24%) patients were female. 846 (58%) patients had no intubation, 241 (17%) patients were intubated for 1-7 days and 113 (7,8%) patients were intubated for more than 7 days. The number of patients who arrived outside working hours — on Saturday or Sunday or after 5 pm or before 8 am were 1,042 (72%). 1,064 (73%) patients were equal to or less than 7 days in the ICU, and 385 (27%) patients were more than 7 days in the ICU. 1,080 (75%) patients had an ASA-score of 1-2 before arrival to the hospital, and 369 (25%) patients had an ASA-score of 3-7 before arrival to the hospital. 286 (20%) patients died within 30 days after hospitalization.

Table 2 shows the unadjusted and adjusted associations of the selected
patient and process factors in relation to OFI. In the unadjusted
analysis the factors that were significantly associated with the
presence of OFI were: Revised Trauma Score `r inline_text(table3a, variable = RTS)`,
≤ 7 days in the ICU `r inline_text(table3a, variable = daysinICU, level = "≤ 7 days")` and death within 30 days after hospitalization `r inline_text(table3a, variable = Survival, level = "Dead")`.

In the adjusted analysis the following factors demonstrated significant
association with OFI: Revised Trauma Score `r inline_text(table3b, variable = RTS)` and ≤ 7 days in the ICU `r inline_text(table3b, variable = daysinICU, level = "≤ 7 days")`.

RTS and ≤ 7 days in the ICU were significantly associated with increased odds of OFI in both the
unadjusted and adjusted analyses.

Sex, Age, Intubation, ISS, time to first CT, on duty and ASA preinjury were not significantly associated with OFI in the unadjusted or the adjusted analyses. Female sex, intubation > 7 days, > 7 days in the ICU, ASA preinjury 1-2 and survival 30 days after hospitalisation could not be analysed with logistic regression.

@@

We found that RTS and ≤ 7 days in the ICU were associated with higher odds of OFI. Previous
research has shown that ...

@@

Death within 30 days after hospitalisation was associated with OFI in the unadjusted analysis but not in the
adjusted analysis.

@@

The study is conducted on 143 outcomes of OFI. There were few outcomes because
we included only those who were admitted to the ICU, \> 14 years old,
not dead on arrival and had a registration for the presence or absence
of OFI. The external validity is therefore compromised due to the
limited size of the Swedish database. However, ...
